### 2018-05-25 evaluation.tex
Add citation to Top500 website

We implement SCP in the OpenBLAS~\cite{openblas} library version 0.3.0-dev,
and evaluate it on a Phytium 2000+ processor.
The Phytium 2000+ processor is an emerging high-performance
64-core processor based on ARM's AArch64 architecture.
The 64 cores are organized into 16 clusters with each
cluster containing 4 cores.
The structure of the cluster is almost the same with
the contrived 4-core processor in Figure.~\ref{fig:hierachy}
except that L2 caches of all 16 clusters connect to the main memory
with hardware coherence.
Table.~\ref{tab:cluster} lists architectural parameters of the cores and caches.
We restrict our evaluation to DGEMM,
as in prior work~\cite{blispar,augem,poetmicro}, for two reasons.
First, the basic idea behind SCP applies to other
variants of GEMM such as SGEMM, CGEMM and ZGEMM.
Second, the LINPACK benchmark, which is used to build the
TOP500 list of world's most powerful supercomputers (FIXME citation),
relies on the DGEMM variant.

>>>>

We implement SCP in the OpenBLAS~\cite{openblas} library version 0.3.0-dev,
and evaluate it on a Phytium 2000+ processor.
The Phytium 2000+ processor is an emerging high-performance
64-core processor based on ARM's AArch64 architecture.
The 64 cores are organized into 16 clusters with each
cluster containing 4 cores.
The structure of the cluster is almost the same with
the contrived 4-core processor in Figure.~\ref{fig:hierachy}
except that L2 caches of all 16 clusters connect to the main memory
with hardware coherence.
Table.~\ref{tab:cluster} lists architectural parameters of the cores and caches.
We restrict our evaluation to DGEMM,
as in prior work~\cite{blispar,augem,poetmicro}, for two reasons.
First, the basic idea behind SCP applies to other
variants of GEMM such as SGEMM, CGEMM and ZGEMM.
Second, the LINPACK benchmark, which is used to build the
TOP500 list of world's most powerful supercomputers~\cite{top500},
relies on the DGEMM variant.
